### 2019-05-13 Writeup/PERT_Paper_Draft1.tex
Add branch and bound rules

	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of EOIT\_3SAT, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\). Since we have a total of \(B = 2m\) units of resource, we can crash all of those \(c\)-activities to achieve a project length of \(2\). This means that we can transform an EOIT\_3SAT problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above. If we can find a feasible EOIT\_3SAT assignment, it is possible to obtain a project length less than or equal to 2. Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption. We first formally define the project crashing decision problem under a stochastic disruption:

@@

		For an instance of the EOIT\_3SAT problem, we construct the corresponding project crashing decision problem under a stochastic disruption: let \(\Omega = \{1\}\), \(H^1 = 0\), \(\mathcal{T} = 2\), and the precedence relationships, the crashing options and budget are constructed by the process shown in the Section~\ref{sec:nphard}. This decision problem has a solution if and only if the given instance of EOIT\_3SAT problem has a solution.

@@

		%We first show that any instance of the project crashing decision problem is constructed in time that is polynomial in the length of the given instance of EOIT\_3SAT, and has a length that is polynomially related to the length of that instance. 
		Suppose the EOIT\_SAT problem has \(n\) variables and \(m\) clauses, the constructed activity network for the project crashing problem has \(4n + 3m + 1\) activities and \(5n + 12m\) arcs, which are both polynomial in the size of the original EOIT\_SAT problem. And all numbers in the project crashing decision problem are smaller than a constant, \(2\).\\
		(\(\implies\)) Suppose the EOIT\_SAT instance has a solution. We have shown that we can start every activity as early as possible, and spend the budget to crash all \(c\)-activities which correspond to the literals with FALSE assignment and have the start time at \(2\). \\
		(\(\impliedby\)) Suppose the project crashing decision problem has a solution \((\hat{t},\hat{x},\hat{G})\) where \(t_T = 2\). By Lemma~\ref{lemma:onlyOne} we know that for each clause there are at most one \(c\)-activity that can start at time \(1\), which means in total there must be at least \(2m\) number of \(c\)-activities with a start time later than \(2\). Since the crashing budget is exactly \(2m\), if there are more than \(2m\) \(c\)-activities that starts after time \(2\), the project length will be larger than 2, which means that there are exactly \(2m\) number of \(c\)-activities starting at time \(2\). This is equivalent to that exactly one \(c\)-activity in each of the \(m\) clauses starts at time \(1\). From Lemma~\ref{lemma:iff} we can directly obtain the result that for each clause there is exactly one variable to which the truth assignment is TRUE, which is essentially a solution to the EOIT\_3SAT instance.\\

@@

		EOIT\_3SAT is a NP-complete problem~\cite{Garey1979ComputersAI}. The project crashing decision problem under a stochastic disruption in NP, since we can check in \(O(n^2)\) to check whether a given input is feasible and has \(t_T \leq \mathcal{T}\). This complete the proof that the project crashing decision problem under a stochastic disruption is NP-complete.

@@

	In this section, we show examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, which is different from the deterministic problem. In the deterministic project crashing problem, all activities on the critical path should start as soon as possible. However, with a stochastic disruption, it might be optimal to delay the start of some activities. Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\). \\
	It is obvious that the delay can possibly be beneficial if \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\). We use a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption, a.k.a., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\). Suppose we have a project with three activities in a serial network form. Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3. The structure of the project is displayed as follows. We add a dummy activity ``T" to represent the end of the project. The total crashing budget is \(1\). 

@@

		\includegraphics[width=0.8\textwidth]{serial3}
		\caption{Example of a 3-activity project}
		\label{fig:serial3}

@@

	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\). There is only one crashing option for each activity, so we omit the subscript to index the crashing options. We use \(e_i = 0.5\) for all \(i \in I\). The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\). The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario. Suppose the disruption does not affect activity 1, \(d_1^1 = 0\), increases the duration of activity 2 by \(0.1\), \(d_2^1 = 0.1\), and increases the duration of activity 3 by \(6\), \(d_3^1 = 6\). We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\). There we can observe whether the disruption happens. If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise, it is optimal to crash activity 2 with \(1\) amount of resource. The expected total project span is \(23.4\), as the optimal project span given no disruption is \(21.1\) and that under disruption is \(25.7\). If every activity starts as soon as possible, like in the deterministic problem, we cannot observe whether the disruption happens or not prior to the start of activity 2. Under this condition, the best solution is to crash activity 2 with \(1\) amount of crashing resource, and the optimal expected project span is \(24\), larger than \(23.4\). \\

@@

	Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished.  We summarize the reasons for such delay include:

@@

	In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path. We present the following example to showcase this property. Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}. The nominal duration of two activities is \(D_1 = 3, D_2 = 4\). The disruption does not affect the duration of activity 1, as \(d_1 = 0\), and lengthens the activity 2 by a random variable distributed in a uniform distribution with upper bound \(10\) and lower bound \(0\), as \(d_2 \sim \mathcal{U}(0,10)\). The crashing option setting is the same as the previous example, as there is only one crashing option for each activity and \(e_i = 0.5, \forall i \in I\). The total budget \(B = 1\).
			\includegraphics[width=0.8\textwidth]{2act}
			\caption{Left: an illustration of a 2-activity project; right: probability distribution function of disruption time.}
			\label{fig:2act}
	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\). Activity 1 starts at time \(t_1 = 0\) and activity 2 starts at time \(t_2 = 1.5\). The optimal expected project span is \(\mathbb{E}[t_T] = 6.5\). We can compare an alternative solution which crash activity 2 with one unit of resource, which has a longer expected duration. Crashing activity 2 matches the intuition from the deterministic case where on the critical path the activities with longer expected duration are prioritized. However, in this case with a stochastic disruption, the latter solution (\(t_1 = 0, t_2 = 3, x_1 = 0, x_2 = 1\)) yields a longer expected project span as \(\mathbb{E}[t_T] = 7.5\). The reason behind this gap is that by crashing activity 1 with one unit amount of resource, the probability of activity 2 starting before the disruption increases to \(0.8\), which prevents activity 2 from seeing the increased duration. \\
	These examples above indicate that the crashing optimization problem with stochastic disruption has complicated nature. The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.
	%\textcolor{blue}{NP-hardness proof.}
	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.

@@

		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} H^{\bar{\omega}^q} F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
		& G_i H^\omega - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\

@@

>>>>

	\noi A direct result from Lemma~\ref{lemma:iff} shows if there exists a truth assignment that meets the requirement of \verb|EOIT_3SAT|, there are at most \(2m\) number of \(c\)-activities (2 per clause) that has to start after time \(2\). Since we have a total of \(B = 2m\) units of resource, we can crash all of those \(c\)-activities to achieve a project length of \(2\). This means that we can transform an \verb|EOIT_3SAT| problem to a project crashing decision problem under a stochastic disruption using the activity network construction process above. If we can find a feasible \verb|EOIT_3SAT| assignment, it is possible to obtain a project length less than or equal to 2. Next, we show the formal NP-hardness proof of the project crashing problem with a stochastic disruption. We first formally define the project crashing decision problem under a stochastic disruption:

@@

		For an instance of the \verb|EOIT_3SAT| problem, we construct the corresponding project crashing decision problem under a stochastic disruption: let \(\Omega = \{1\}\), \(H^1 = 0\), \(\mathcal{T} = 2\), and the precedence relationships, the crashing options and budget are constructed by the process shown in the Section~\ref{sec:nphard}. This decision problem has a solution if and only if the given instance of \verb|EOIT_3SAT| problem has a solution.

@@

		%We first show that any instance of the project crashing decision problem is constructed in time that is polynomial in the length of the given instance of \verb|EOIT_3SAT|, and has a length that is polynomially related to the length of that instance. 
		Suppose the \verb|EOIT_3SAT| problem has \(n\) variables and \(m\) clauses, the constructed activity network for the project crashing problem has \(4n + 3m + 1\) activities and \(5n + 12m\) arcs, which are both polynomial in the size of the original \verb|EOIT_3SAT| problem. And all numbers in the project crashing decision problem are smaller than a constant, \(2\).\\
		(\(\implies\)) Suppose the \verb|EOIT_3SAT| instance has a solution. We have shown that we can start every activity as early as possible, and spend the budget to crash all \(c\)-activities which correspond to the literals with FALSE assignment and have the start time at \(2\). \\
		(\(\impliedby\)) Suppose the project crashing decision problem has a solution \((\hat{t},\hat{x},\hat{G})\) where \(t_T = 2\). By Lemma~\ref{lemma:onlyOne} we know that for each clause there are at most one \(c\)-activity that can start at time \(1\), which means in total there must be at least \(2m\) number of \(c\)-activities with a start time later than \(2\). Since the crashing budget is exactly \(2m\), if there are more than \(2m\) \(c\)-activities that starts after time \(2\), the project length will be larger than 2, which means that there are exactly \(2m\) number of \(c\)-activities starting at time \(2\). This is equivalent to that exactly one \(c\)-activity in each of the \(m\) clauses starts at time \(1\). From Lemma~\ref{lemma:iff} we can directly obtain the result that for each clause there is exactly one variable to which the truth assignment is TRUE, which is essentially a solution to the \verb|EOIT_3SAT| instance.\\

@@

		\verb|EOIT_3SAT| is a NP-complete problem~\cite{Garey1979ComputersAI}. The project crashing decision problem under a stochastic disruption in NP, since we can check in \(O(n^2)\) to check whether a given input is feasible and has \(t_T \leq \mathcal{T}\). This complete the proof that the project crashing decision problem under a stochastic disruption is NP-complete.

@@

	In this section, we show two examples of serial activity networks to illustrate the nature of the project crashing problem under stochastic disruption, and its distinctions from the deterministic problem. In the deterministic project crashing problem, all activities on the critical path should start as soon as possible. However, with a stochastic disruption, it might be optimal to delay the start of some activities. In addition, under a stochastic disruption, it is possible that on a critical path, an activity with a smaller expected length is crashed with a larger amount of resource, while in the deterministic case, it is always optimal to start crashing from the longest one on the critical path. We use the following two examples to show that the deterministic optimal solution could be significantly inferior in the stochastic setting because of those two properties. \tcb{Starting from this section, we assume that required separations between an activity \(i\) and all its successors \(k\) are the same for simplicity; i.e., for every activity \(i\) we use \(D_i\) to represent the duration of activity \(i\) and \(d_i^\omega\) to denote the change of duration due to the disruption scenario \(\omega\):
		& D_{ik} = D_i \qquad \qquad \forall (i,k) \in \cA\\
		& d^{\omega}_{ik} = d^{\omega}_i \qquad \qquad \forall (i,k) \in \cA, \omega \in \Omega.
	\end{align*}}

@@

		\includegraphics[width=0.6\textwidth]{serial2}
		\caption{Example of a 2-activity serial network project}
		\label{fig:serial2}

@@

	\begin{example} \label{eg:delay}
		It is obvious that the delay can possibly be beneficial when \(d_i^\omega < 0\) for some \(i \in I\) and \(\omega \in \Omega\) because the decrease in duration may outweigh the length of delay to move the start of activity \(i\) after the disruption. Therefore, we set up a serial activity network to show the possibility of beneficial delay, even if all activities are lengthened by the disruption; i.e., \(d_i^\omega > 0, \forall i \in I, \omega \in \Omega\). Consider a network with two activities in series, as shown in Figure~\ref{fig:serial2}. Suppose we have a parameter \(k > 4\). In this example, $I=\{S,1,2,T\}$ with nominal durations $D_1 = k$ and $D_2 = 1$. We assume only one crashing option for each activity, and so we omit index $j$. We let $e_1=e_2=1 - \frac{1}{2k}$, assume $b_i=1$ for all $i \in I$, and we let $B=1$. Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=1 - \frac{1}{k}$, or we have a disruption that occurs at time $\varepsilon \leq \frac{1}{2}$ with probability $p^1=\frac{1}{k}$. If a disruption occurs, the nominal activity durations are lengthened by $d_1 = k$ and $d_2 = (k - 1)^2$. \\

@@

		If we start each activity without delay, then \(t_1 = 0,\ x_1=x_1^1\), and for any \(x_1 \leq 1\), \(t_2 \geq \frac{1}{2} \geq D_1(1 - e_1 x_1) \), which means activity \(2\) will start after the disruption. Since \(k > 1\), the expected duration of activity \(1\), $D_1 = k$ is greater than the expected duration of activity 2, $ D_2 + p^1 d_2 = 1 + \frac{1}{k} (k-1)^2 = k - 1 + \frac{1}{k}$. As a result, it is optimal to spend the entire budget on activity \(1\): $x_1=x_1^1=1$ and $x_2=x_2^1=0$, and the expected project duration is: 
			\label{nodelay}
			&D_1 (1 - e_1 x_1) + p^0 D_2 + p^1 (D_2 + d_2) \\
			= & k \left(1 - (1 - \frac{1}{2k})\cdot 1 \right) + (1 - \frac{1}{k}) \cdot 1 + \frac{1}{k} \left(1 + (k -1)^2\right) \\
			= & k - \frac{1}{2} + \frac{1}{k}.
		On the other hand, if we delay the start of activity 1 until $t_2= \varepsilon$ then $x_1$ and $x_1^1$ need not be equal. Since for \(k > 2 + \sqrt{2}\), $k = D_1 > D_2 = 1$ and $(k - 1)^2 + 1 = D_2+d_2 > D_1 + d_1 = k + k$, we have $x_2=1$ and $x_3^1=1$ in an optimal solution, and the expected duration is:
			\begin{align}\label{delay}
				&\varepsilon + p^0 \left[D_1 \cdot \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) + D_2 \right]  + p^1 \left[(D_1 + d_1) + \left(1 - (1 - \frac{1}{2k}) \cdot 1 \right) (D_2 + d_2) \right]\\
				= & \varepsilon + \frac{k - 1}{k} \left(k \cdot \frac{1}{2k} + 1\right) + \frac{1}{k} \left[ (k + k) + \frac{1}{2k} \left((k-1)^2 + 1\right) \right] \\
				= & \varepsilon + 4 - \frac{5}{2k} + \frac{1}{k^2}.
		In the example above, as \(k \to +\infty\), the project span without delay approaches \(+\infty\), but the project span with delay has a constant limit \(\varepsilon + 4\). This example shows that with the possibility that a rare but pathological disruption may occur, it is infinitely better to delay the start of some activities. In summary, the reasons for such delay include:

@@

		Because it is possible for an optimal crashing plan to contain a delay for some activities, we have to set up decision variables \(t_i,\ \forall i \in I\), as the start time of each activity, rather than assume that each activity starts as soon as all of its predecessors are finished. 
	\end{example}
	\begin{example} \label{eg:short}
		Consider the same network with two activities in series as shown in Figure~\ref{fig:serial2}. Let $D_1$ and $D_2$ denote the two durations with $D_2 > D_1$. Assume $d_1=0$, $d_2 > 0$, $e_1=e_2=\frac{1}{2}$, and $B=1$. Set $\Omega=\{1\}$ so that either we have no disruption, $p^0=\frac{1}{2}$, or we have a disruption that occurs at time $\frac{1}{2}D_1$ with probability $p^1=\frac{1}{2}$. Here, the optimal solution is to crash the shorter activity, i.e., $x_1=1$, which yields an expected project span of $\frac{1}{2}D_1 + D_2$ with start times $t_1=0$ and $t_2=\frac{1}{2}D_1$. In contrast, if $0 \le x_1 < 1$ then the expected duration is $D_1 (1-\frac{1}{2} x_1) + (D_2 + d_2)(1-\frac{1}{2} x_2)$, so that the ratio of the objective functions grows arbitrarily large as $d_2$ grows. The intuition behind crashing the shorter activity is that it allows us to initiate activity 2 in time to avoid having to incur delay $d_2$.
		%\\
		%\newline
		%This example shows that because the disruption may significantly change the duration of an activity, crashing shorter activities at the beginning of the project to prevent disruption may yield a significantly better result than crashing longer activities closer to the end of the project.
	\end{example}

	\noi Example~\ref{eg:delay} and~\ref{eg:short} indicate that the crashing optimization problem with stochastic disruption has complicated nature. The intuition of deterministic crashing optimization problem does not apply here, and we need a math program model as~\eqref{prob:extensive} to solve for the best crashing plan.

%	Therefore, it is necessary to have decision variable \(t_i, \forall i \in I\) in model~\eqref{prob:extensive} in addition to the crashing decision variable \(x_{ij}, \forall i \in I, j \in J_i\). \\
%	\newline
%	  Suppose we have a project with three activities in a serial network form. Activity 1 must finish before the start of activity 2 and the activity 2 must finish before the start of activity 3. The structure of the project is displayed as follows. We add a dummy activity ``T" to represent the end of the project. The total crashing budget is \(1\). 
%	
%	\noi In this example, \(I=\{1,2,3,T\}\), \(D_1=9\), \(D_2=10\), and \(D_3=7\). There is only one crashing option for each activity, so we omit the subscript to index the crashing options. We use \(e_i = 0.5\) for all \(i \in I\). The probability of the disruption not occurring is \(p^0=\frac{1}{2}\), and if a disruption occurs, it will occur at the time \(H^2 = 9.1\). The set of scenario \(\Omega = \{1\}\), where scenario 1 represents the disruption scenario. Suppose the disruption does not affect activity 1, \(d_1^1 = 0\), increases the duration of activity 2 by \(0.1\), \(d_2^1 = 0.1\), and increases the duration of activity 3 by \(6\), \(d_3^1 = 6\). We can see it is optimal to delay the start of activity 2 to \(t_2 = 9.1\). There we can observe whether the disruption happens. If the disruption occurs, it is optimal to spend the entire budget to crash activity 3, and otherwise, it is optimal to crash activity 2 with \(1\) amount of resource. The expected total project span is \(23.4\), as the optimal project span given no disruption is \(21.1\) and that under disruption is \(25.7\). If every activity starts as soon as possible, like in the deterministic problem, we cannot observe whether the disruption happens or not prior to the start of activity 2. Under this condition, the best solution is to crash activity 2 with \(1\) amount of crashing resource, and the optimal expected project span is \(24\), larger than \(23.4\). \\
%	\newline
%	 We present the following example to showcase this property. Suppose we have a two-activity serial network, and the disruption time follows a probability distribution shown in Figure~\ref{fig:2act}. The nominal duration of two activities is \(D_1 = 3, D_2 = 4\). The disruption does not affect the duration of activity 1, as \(d_1 = 0\), and lengthens the activity 2 by a random variable distributed in a uniform distribution with upper bound \(10\) and lower bound \(0\), as \(d_2 \sim \mathcal{U}(0,10)\). The crashing option setting is the same as the previous example, as there is only one crashing option for each activity and \(e_i = 0.5, \forall i \in I\). The total budget \(B = 1\).
%	\noi In this example, the optimal solution is to crash activity 1 with one unit of resource, i.e.\,\(x_1 = 1, x_2 = 0\). Activity 1 starts at time \(t_1 = 0\) and activity 2 starts at time \(t_2 = 1.5\). The optimal expected project span is \(\mathbb{E}[t_T] = 6.5\). We can compare an alternative solution which crash activity 2 with one unit of resource, which has a longer expected duration. Crashing activity 2 matches the intuition from the deterministic case where on the critical path the activities with longer expected duration are prioritized. However, in this case with a stochastic disruption, the latter solution (\(t_1 = 0, t_2 = 3, x_1 = 0, x_2 = 1\)) yields a longer expected project span as \(\mathbb{E}[t_T] = 7.5\). The reason behind this gap is that by crashing activity 1 with one unit amount of resource, the probability of activity 2 starting before the disruption increases to \(0.8\), which prevents activity 2 from seeing the increased duration. \\
%	\newline

	%\textcolor{blue}{NP-hardness proof.}
	%Add the conclusion of consistency. Add the proof of consistency. Prove the inconsistency of the stratified sampling method.

@@

		\text{s.t.} \quad & H^\omega + \sum_{q \in \mathcal{Q}_i} \bar{H}^q F_i^q - H^\omega G_i \geq \hat{t}_i \qquad \qquad \forall i \in I \label{cons:sFG1t}\\
		& H^\omega G_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q F_i^q \leq \hat{t}_i - \sum_{q \in \mathcal{Q}_i} \underbar{H}^q \hat{y}_i^q \qquad \qquad \forall i \in I \label{cons:sFG2t}\\

@@

		& 0 \leq F_i^q \leq 1 \qquad \qquad \forall \,i \in I, q \in \mathcal{Q}_i\\

### 2019-05-13 Writeup/PERT_Paper_Draft2.tex
Add branch and bound rules

			Notice that the inequality~\eqref{cons:case2eqn2} is always weaker than~\eqref{cons:case2eqn1} because the right-hand side of~\eqref{cons:case2eqn2} is smaller than 0 while the right-hand side of~\eqref{cons:case2eqn1} is positive. Similar to Case 1, the lower bound increases compared to using a large \(M\) and the upper bound is \(1\), and we achieve a tightened relaxation.

@@

		thus, we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\). Therefore, inequality~\eqref{cons:gglb} holds. Furthermore, the cut generated at partition \(\mathcal{P}^\ell\) is

>>>>

			Notice that the inequality~\eqref{cons:case2eqn2} is strictly weaker than~\eqref{cons:case2eqn1} because the right-hand side of~\eqref{cons:case2eqn2} is smaller than 0 while the right-hand side of~\eqref{cons:case2eqn1} is positive. Similar to Case 1, the lower bound increases compared to using a large \(M\) and the upper bound is \(1\), and we achieve a tightened relaxation.

@@

		we obtain a feasible solution \((t^{\omega,*},x^{\omega,*},G^{\omega,*},\tilde{F}^{\omega,*})\) to the recourse problem corresponding to the partition \(\mathcal{P}^\ell\). Therefore, inequality~\eqref{cons:gglb} holds. Furthermore, the cut generated at partition \(\mathcal{P}^\ell\) is
